---
title: "Project 2"
author: "Tess Steplyk"
date: "12/21/2016"
output: html_document
---

``````{r, echo=FALSE, include=FALSE, cache=FALSE}
setwd("/Users/TessSteplyk/Google Drive/Stat461")
library(fBasics)
library(quantmod)
library(rugarch)
library(TSA)
```

```{r}
require(quantmod)
getSymbols("TRV", from="2006-01-01", to="2016-01-01")
head(TRV)
tail(TRV)
dim(TRV)
chartSeries(TRV$TRV.Adjusted, name= "Closing Prices TRV" , theme="white") #plot adjusted stocks
TRV.rtn = diff(log(TRV$TRV.Adjusted))[-1,] #calc log rtn based on adj prices
```


QQ for tGARCH
```{r}
return=as.vector(diff(log(TRV$TRV.Adjusted))[-1,])
######GARCH(1,1)#######
spec3=ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), 
  mean.model = list(armaOrder = c(0, 2)), 
  distribution.model = "sstd")
fit3 = ugarchfit(return, spec=spec3)
plot(fit3, which=9); plot(fit3, which=3)
fitted.sigma = unclass(sigma(fit3))[,1]
forecast=ugarchforecast(fit3, n.ahead=60) # 60-step ahead forecast with refined model
plot(forecast, which=1) # plot for predicted mean value +/- predicted volatility for the next 10 days
plot(forecast, which=3) # plot for predicted sigma for the next 10 days

#######tGARCH(1,2)#######
tspec3=ugarchspec(
  variance.model = list(model = "fGARCH", submodel="TGARCH", garchOrder = c(1, 2)), 
  mean.model = list(armaOrder = c(0, 2)), 
  distribution.model = "sstd")
tfit3 = ugarchfit(return, spec=tspec3)
plot(tfit3, which=9); plot(tfit3, which=3)
fitted.sigma12 = unclass(sigma(tfit3))[,1]
forecast12=ugarchforecast(tfit3, n.ahead=60) # 60-step ahead forecast with refined model
plot(forecast12, which=1) # plot for predicted mean value +/- predicted volatility for the next 10 days
plot(forecast12, which=3) # plot for predicted sigma for the next 10 days

####tGARCH(2,2)#####
tspec2=ugarchspec(
  variance.model = list(model = "fGARCH", submodel="TGARCH", garchOrder = c(2, 2)), 
  mean.model = list(armaOrder = c(0, 2)), 
  distribution.model = "sstd")
tfit2 = ugarchfit(return, spec=tspec2)
plot(tfit2, which=9); plot(tfit2, which=3)
fitted.sigma22 = unclass(sigma(tfit2))[,1]
forecast22=ugarchforecast(tfit2, n.ahead=60) # 60-step ahead forecast with refined model
plot(forecast22, which=1) # plot for predicted mean value +/- predicted volatility for the next 10 days
plot(forecast22, which=3) # plot for predicted sigma for the next 10 days


round(coef(tfit3),6)
```

tGARCH Forecast / Black Scholes
```{r}

```

Call/Put
```{r}
call.price <- function(x = 1, t = 0, T = 1, r = 1, sigma = 1, K=1){
  d2<-(log(x/K)+(r-0.5*sigma^2)*(T-t))/(sigma*sqrt(T-t)) 
  d1<-d2+sigma*sqrt(T-t) 
  x*pnorm(d1)-K*exp(-r*(T-t))*pnorm(d2)
}

put.price <- function(x = 1 ,t = 0, T =1 , r = 1, sigma=1, K=1){
  d2<-(log(x/K)+(r-0.5*sigma^2)*(T-t))/(sigma* sqrt(T-t)) 
  d1<-d2+sigma*sqrt(T-t) 
  K*exp(-r*(T-t))*pnorm(-d2)-x*pnorm(-d1)
}

# specify parameters
S0 <- as.numeric(TRV.rtn[length(TRV.rtn)]) ; K <- 0:80; r <- 0.06; T <- 60; sigma <- 0.1
C <-call.price(x=S0, t=0, T=T, r=r, K=K, sigma=sigma)
P <-put.price(x=S0, t=0, T=T , r=r, K=K, sigma=sigma)
par(mfrow=c(1,2))
plot(K,C,type="l", xlab="strike price K", ylab="fair premium for call option")
plot(K,P,type="l", xlab="strike price K", ylab="fair premium for put option")

```

Black-Scholes Estimations

new.sigma = unclass(sigma(forecast)[,1])
new.fitted = unclass(fitted(forecast)[,1])
S0 = as.numeric(TRV.rtn[length(TRV.rtn)])
T = 60
r = new.fitted[60]
volatility = new.sigma[60]
Sto = S0*0.6
Sfr = S0*1.6
sigma=0.1
K = seq(Sto, Sfr, by = sigma)
d1 = (log(S0/K) + (r + (volatility^2)/2)*T)/(volatility*sqrt(T))
d2 = (log(S0/K) + (r - (volatility^2)/2)*T)/(volatility*sqrt(T))
C0 = S0*pnorm(d1)-K*exp(-r*T)*pnorm(d2)
P0 = K*exp(-r*T)*pnorm(-d2)-S0*(pnorm(-d1))
profit = pmax((S0*exp((r - (volatility^2)/2)*T) - K), 0) - C0

par(mfrow = c(1,3), cex = 0.75)
plot(K, C0, type = "l", xlab="Strike Price", ylab="Fair Price", main="Risk Neutral Pricing of Call") 
plot(K, pnorm(d2), type = "l", ylab = "Probability", xlab="Strike Price", main="P(Call exercised) vs. K")
plot(K, profit, main="Predicted Profit", ylab="Profit", xlab="Strike Price", type = "l")

ST = S0*exp((r - (volatility^2)/2)*T)

profit = pmax((K - S0*exp((r - (volatility^2)/2)*T)), 0) - P0
par(mfrow = c(1,3), cex = 0.75)
plot(K, P0, type = "line", xlab="Strike Price", ylab="Fair Price", main="Risk Neutral Pricing of Put") 
plot(K, pnorm(-d2), type = "l", ylab="Probability", xlab="Strike Price", main = "P(Put Exercised) vs. K") 
plot(K, profit, type = "l", main = "Predicted Profit")

v = coef(tfit3)[length(coef(tfit3))]
last.n = length(TRV.rtn)
VaRm = unclass(coef(tfit3)[1] + qt(0.95, v)*sigma(tfit3)[last.n])[1]
ESm = unclass(coef(tfit3)[1] + sigma(tfit3)[last.n][1]*dt(qt(0.95, v), v)/0.05*((v + dt(qt(0.95, v), v)^2)/(v - 1)))[1]
cash.varm = VaRm * S0
cash.esm = ESm * S0
