---
title: "Project"
author: "Tess Steplyk"
date: "11/29/2016"
output: html_document
---

``````{r, echo=FALSE, include=FALSE, cache=FALSE}
setwd("/Users/TessSteplyk/Google Drive/Stat461")
library(fBasics)
library(quantmod)
library(rugarch)
library(TSA)
```

```{r}
getSymbols("TRV") #Travlerers Prop/Casual
getSymbols("TRV", from="2006-01-01", to="2016-01-01")
head(TRV)
tail(TRV)
dim(TRV)
chartSeries(TRV$TRV.Adjusted, name= "Closing Prices TRV" , theme="white") #plot adjusted stocks
TRV.rtn = diff(log(TRV$TRV.Adjusted))[-1,] #calc log rtn based on adj prices
chartSeries(TRV.rtn, name= "Log Returns TRV", theme="white")
TRV.srtn = exp(TRV.rtn)-1
chartSeries(TRV.srtn, name= "Simple Net Returns TRV", theme="white")

#####################

sym = TRV.rtn[15,]
s = sym/sqrt(6/length(TRV.rtn))
s
ps = 2*pnorm(s, lower.tail = FALSE)
ps
kurt = TRV.rtn[16,]
kurt
k = (kurt - 3)/sqrt(24/length(TRV.rtn))
k
pk = 2*pnorm(k, lower.tail = FALSE)
pk
```


```{r}
basicStats(TRV.rtn)
normalTest(as.vector(TRV.rtn), method="jb")
skewness(TRV.rtn)/sqrt(6/length(TRV.rtn))
kurtosis(TRV.rtn)/sqrt(24/length(TRV.rtn))
```

ACF PACF
```{r}
return=as.vector(diff(log(TRV$TRV.Adjusted))[-1,])
par(mfrow=c(1,2))
acf(TRV.rtn); pacf(TRV.rtn)

acf(TRV.rtn)$acf #estimated acf values for all 35 legs, serial correlations do not appear to be significant for the first 10 lags

log(length(TRV.rtn)) # choose m=8 at which test has better power performance

Box.test(TRV.rtn, lag=34) # Box-Pierce test: reject null, v small p-val

Box.test(TRV.rtn, lag=34, type="Ljung") # Ljung-Box test: reject null, v small p-val

eacf(TRV.rtn)

m=eacf(TRV.rtn, 7, 13)

print(m$eacf[0:7, 0:13], digits=1)


model=arima(TRV.rtn, order=c(2,0,0))
model
plot(na.omit(model$residuals), ylab="residuals")
acf(na.omit(model$residuals))
```


Ljung #APPENDIX
```{r}
return=as.vector(diff(log(TRV$TRV.Adjusted))[-1,])
spec1=ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 0)), 
  mean.model = list(armaOrder = c(0, 2), include.mean=FALSE), 
  fixed.pars=list(ma1=0),
distribution.model = "sstd") # specify model structure
m1=ugarchfit(return,spec=spec1) # fit ARMA(0,2)-ARCH(1) model show(m1) 
m1# show model fit

######### estimated volatilities ######### 
plot((sigma(m1))^2, type="b",
     ylab="Fitted Conditional Volatility", xlab="Time", main="Estimated Volatility")

infocriteria(m1) # information criteria list (AIC/BIC/SIC)

m2=ar(as.vector(return), method = "mle")
m2$order #11
plot(0:12, m2$aic, type ="o", xlab="order", ylab="AIC") #aic lag





acf(TRV.rtn) #lag tails off at 12
pacf(TRV.rtn)


m3=ar(as.vector(TRV.rtn), method="mle") # automatic AR fitting using AIC criterion 
m3$order # lag chosen by AIC criterion, AR(4) model minimizes AIC
names(m3)
print(m3$aic,digits=3) # print out AIC values as a function of P for AR(P) model
par(mfrow=c(1,1))
plot(0:12,m3$aic,type="o",xlab="order",ylab="aic") # plot AIC as a function of lag
m3

m4=arima(TRV.rtn,order=c(4,0,0)) # another way to fit the model with specified lags 
m4 # model summary
names(m4)


#########Stationarity#########
options(digits=4)
p1=c(1,-m4$coef[1:4]) # extract estimated coefficients from model output 
p1
roots=polyroot(p1) # solutions to characteristic equation 
roots
c.roots=1/roots # characteristic roots are inverses of solutions above 
c.roots
Mod(c.roots) # modulus of characteristic roots are less than 1, process is stationary

############Remove insignificant parameters.#########
m4$coef #estim coeff
vcov(m4) # variance-covariance matrix of estimated coefficients
m4$coef/sqrt(diag(vcov(m4))) # check insignificant coefficients
m5=arima(TRV.rtn,order=c(4,0,0),fixed=c(NA,NA,0,NA,0)) # remove insignificant coefficients and refit 
m5 # model summary
par(mfrow=c(1,2))
plot(na.omit(m5$resid), ylab="residuals") # residual series still doesn't appears to have constant mean (close to 0)
acf(na.omit(m3$resid), lag=11, main="ACF of residuals") # acf of residuals, no significant serial correlation
Box.test(na.omit(m3$resid), lag=34, fitdf=11) # Box Pierce test
Box.test(na.omit(m3$resid), lag=34, fitdf=11, type="Ljung") # Ljung Box test


pred<-predict(m5,n.ahead=40) # 40 step ahead forecast 
plot(as.vector(TRV.rtn)[900:1000],xlim=c(1,140),type="l",ylab="",xlab="") # plot last 100 observations 
lines(101:140, pred$pred,col="blue", lwd=2) # add predicted values 
lines(101:140,pred$pred+2*pred$se,col="red",lty=3, lwd=2) # add upper confidence bound for 
lines(101:140,pred$pred-2*pred$se,col="red",lty=3, lwd=2) # add lower confidence bound forpredicted value
```


ARCH Model
```{r}
require(rugarch)
require(quantmod)
return=as.vector(diff(log(TRV$TRV.Adjusted))[-1,])
##################################
# Mean Structure ARMA(2,0) Model #
################################## 
#m1=arima(return,order=c(2,0,0),fixed=c(0,NA,0))
#m1
#par(mfrow=c(1,2))
#acf(m1$residuals^2); pacf(m1$residuals^2)

################################################
# Volatility Structure ARMA(0,4)-ARCH(5) Model #
################################################
# ugarchspec: for specifying model structure.
#             sGARCH stands for standard GARCH model.
#             garchOrder: first number (5 here) corresponds to ARCH order
#             armaOrder: corresponds to orders in ARMA model
#             include.mean: whether to include mean (mu) in the mean structure
#             fixed.pars: fix the following parameters: ma1, ma2, ma3 to be equal to 0
# distribution.model: distribution assumption on error terms (normal here) 
return=as.vector(diff(log(TRV$TRV.Adjusted))[-1,])
spec1=ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(2, 0)), 
  mean.model = list(armaOrder = c(0, 1), include.mean=FALSE), 
  fixed.pars=list(ma1=0),
distribution.model = "norm") # specify model structure
m=ugarchfit(return,spec=spec1) 
show(m)# show model fit
infocriteria(m1)

spec2=ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(2, 0)), 
  mean.model = list(armaOrder = c(0, 0), include.mean=FALSE), 
  fixed.pars=list(alpha3=0),
  distribution.model = "sstd")
m2=ugarchfit(return,spec=spec2)
show(m2)
par(mfrow=c(1,3))
plot(m2, which=9); #plot(m2, which=10); plot(m2, which=11) # check model assumption
ugarchforecast(m2, n.ahead=8) # 8-step ahead forecast with refined model
```

GARCH
```{r}
return=as.vector(diff(log(TRV$TRV.Adjusted))[-1,])
######GARCH#########
spec3=ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), 
  mean.model = list(armaOrder = c(0, 2)), 
  distribution.model = "sstd")
fit3 = ugarchfit(return, spec=spec3)
fit3
infocriteria(fit3)
plot(fit3, which=2)
plot((sigma(fit3))^2, type="b",
     ylab="Fitted Conditional Volatility", xlab="Time", main="Estimated Volatility for GARCH(1,1)")

spec13=ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 2)), 
  mean.model = list(armaOrder = c(0, 2)), 
  distribution.model = "sstd")
fit13 = ugarchfit(return, spec=spec13)

spec23=ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(2, 1)), 
  mean.model = list(armaOrder = c(0, 2)), 
  distribution.model = "sstd")
fit23 = ugarchfit(return, spec=spec23)
fit23


spec22=ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(2, 2)), 
  mean.model = list(armaOrder = c(0, 2)), 
  distribution.model = "sstd")

```
#######iGARCH#######
ispec3=ugarchspec(
  variance.model = list(model = "iGARCH", garchOrder = c(1, 1)), 
  mean.model = list(armaOrder = c(0, 1)), 
  fixed.pars=list(omega=0),
  distribution.model = "sstd")
ifit3 = ugarchfit(return, spec=ispec3)
ifit3
istd.res.3 = return / sigma(ifit3)
```
```{r}
#######tGARCH#######
tspec3=ugarchspec(
  variance.model = list(model = "fGARCH", submodel="TGARCH", garchOrder = c(1, 2)), 
  mean.model = list(armaOrder = c(0, 2)), 
  distribution.model = "sstd")
tfit3 = ugarchfit(return, spec=tspec3)
tfit3
infocriteria(tfit3)
plot(tfit3, which=2)
```
#######mGARCH#######
mspec3=ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 2)), 
  mean.model = list(armaOrder = c(0, 2), archm=T), 
  distribution.model = "sstd")
mfit3 = ugarchfit(return, spec=mspec3)
mfit3
mstd.res.3 = return / sigma(mfit3)
##
#######iGARCH#######
ispec2=ugarchspec(
  variance.model = list(model = "iGARCH", garchOrder = c(1, 1)), 
  mean.model = list(armaOrder = c(0, 2)), 
  fixed.pars=list(omega=0),
  distribution.model = "sstd")
ifit2 = ugarchfit(return, spec=ispec2)
ifit2
```
```{r}
#######tGARCH#######
tspec2=ugarchspec(
  variance.model = list(model = "fGARCH", submodel="TGARCH", garchOrder = c(2, 2)), 
  mean.model = list(armaOrder = c(0, 2)), 
  distribution.model = "sstd")
tfit2 = ugarchfit(return, spec=tspec2)
tfit2
infocriteria(tfit2)
plot(tfit2, which=2)
```
#######mGARCH#######
mspec2=ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(2, 2)), 
  mean.model = list(armaOrder = c(0, 2), archm=T), 
  distribution.model = "sstd")
mfit2 = ugarchfit(return, spec=mspec2)
mfit2
```

QQ for tGARCH
```{r}
tspec3=ugarchspec(
  variance.model = list(model = "fGARCH", submodel="TGARCH", garchOrder = c(1, 2)), 
  mean.model = list(armaOrder = c(0, 2)), 
  distribution.model = "sstd")
tfit3 = ugarchfit(return, spec=tspec3)

plot((sigma(tfit3))^2, type="b",
     ylab="Fitted Conditional Volatility", xlab="Time", main="Estimated Volatility for tGARCH(1,2)")

plot(tfit3, which=9); #plot(tfit3, which=10); plot(tfit3, which=11) # check model assumption


###

tspec2=ugarchspec(
  variance.model = list(model = "fGARCH", submodel="TGARCH", garchOrder = c(2, 2)), 
  mean.model = list(armaOrder = c(0, 2)), 
  distribution.model = "sstd")
tfit2 = ugarchfit(return, spec=tspec2)
plot((sigma(tfit2))^2, type="b",
     ylab="Fitted Conditional Volatility", xlab="Time", main="Estimated Volatility for tGARCH(2,2)")

par(mfrow=c(1,3))
plot(tfit2, which=9); #plot(tfit2, which=10); plot(tfit2, which=11) # check model assumption

```




